---
title: "Developing Data Products Final Assignment"
author: "Heather Meylemans"
date: "1/2/2020"
output:
  slidy_presentation: default
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Coursera Pitch

This is a task for the data science coursera course about developing data products for week 4. As part of this, I have created a shiny app and deployed it on the shiny server. The link is XXXX. The code can be found at XXXXX.

## Overview

The shiny app plots a graph for miles per gallon (mpg) against different variables from the mtcars dataset.

```{r} 
head(mtcars)
```

## UI Code


library(shiny)

shinyUI(fluidPage(
  
  # Application title
  titlePanel("Cars Dataset - Miles per Gallon"),
  
  sidebarPanel(
    
    selectInput("variable", "Variable:", 
                c("Cylinders" = "cyl",
                  "Transmission" = "am",
                  "Gears" = "gear"))
    ),
  
  mainPanel(
    # Output: Formatted text for caption ----
    h3(textOutput("caption")),
    
    # Output: Plot of the requested variable against mpg ----
    plotOutput("mpgPlot")
    )
))

    
    
## Server Code

library(shiny)
library(plotly)

mpgData <- mtcars
mpgData$am <- factor(mpgData$am, labels = c("Automatic", "Manual"))

shinyServer(function(input, output) {
  
  formulaText <- reactive({
    paste("mpg vs ", input$variable)
  })
  
  output$caption <- renderText({
    formulaText()
  })
  
  output$mpgPlot <- renderPlot({
    ggplot(mpgData, aes_string(y=input$variable, x="mpg")) + geom_point()
  })
  
})

